%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Scala Developer} % Job title
    {Capgemini} % Organization
    {Telford, England} % Location
    {Jan. 2021 - Present} % Date(s)
    {
      \raggedright
      \begin{cvitems}
        \item {Developed and optimized frontend designs for HMRC government services, ensuring accessibility, performance, and compliance with UK government standards.}
        \item {Led the enhancement of multiple services across key domains, including Tobacco and Alcohol Customs Duty, Charities Registration, the Covid Furlough Scheme, and Gov Gateway/SCP.}
        \item {Collaborated across cross-functional teams, contributing to both product development and live service maintenance.}
        \item {Designed, maintained, and enhanced automated testing frameworks, improving the efficiency of End-to-End and Performance Load tests.}
        \item {Integrated and optimized various in-house libraries, including encryption utilities and NoSQL Mongo-based backend tools, enhancing system security and scalability.}
        \item {Diagnosed and resolved critical production issues in legacy systems, improving reliability and performance.}
        \item {Implemented real-time monitoring and error diagnostics using Kibana, ensuring system stability across multiple environments.}
        \item {Analyzed and reverse-engineered live service systems to enhance documentation, streamline onboarding, and support knowledge transfer.}
        \item {Provided technical mentorship and facilitated onboarding for new hires and contractors, promoting knowledge sharing and best practices.}
      \end{cvitems}
    }
%---------------------------------------------------------
    \cventry
    {Junior Consultant} 
    {Ten10} 
    {Leeds, England} 
    {Jan. 2019 - Dec. 2021}
    {
      \raggedright
      \begin{cvitems}
        \item {Software consulting specialising in Software Testing.}
        \item {Had software development and testing bootcamps going over Agile, Git, Java, JUnit, JMeter and various other topics, Selenium.}
        \item {On bench studied Python and played with various libaries for 7 months.}
        \item {Also completed ISTQB Testing Foundation and BCS Business Analysis certifications.}
        \item {Built a webscraper, a CNN using Keras API using Tensorflow, studied ML, neural networks and deep learning topics.}
        \item {Was then sent to Capgemini/HMRC to work with Scala and on HMRC Services}
      \end{cvitems}
    }    

%---------------------------------------------------------
\cventry
    {Various part time jobs} 
    {Misc} 
    {Various, Locations} 
    {Jan. 2014 - Dec. 2019}
    {}      

\end{cventries}
