%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Self-Study / Pet Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend \& Backend Development} % Affiliation/role
    {} % Organization (leave empty if not applicable)
    {} % Location (leave empty)
    {} % Dates (leave empty)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Attempted to delve into a distributed full-stack application using Next.js, Scala Typelevel stack, and PostgreSQL.}
        \item {Learned a lot about Docker, Docker network, DockerCLI, docker-compose, and Traefik.}
        \item {Learned a lot about Next.js/React in general.}
        \item {Developed proficency in Typescript.}
        \item {Learned a lot and utilised Github Actions.}
        \item {Explored and integrated various libraries within the React ecosystem, gaining hands-on experience in state management, component design, and API integration.}
        \item {Successfully utilised Tailwind CSS utility classes to streamline styling and improve user experience, with a focus on accessibility and responsive design.}
        \item {Built a backend using the Scala Typelevel stack, leveraging functional programming paradigms for robust and scalable applications.}
        \item {Utilized the Tagless Final pattern, improving abstraction, modularity, and testing capabilities within Scala-based microservices.}
        \item {Forced myself to use Postgresql to develope proficiency in SQL, focusing on database design, query optimization, and indexing strategies for improved performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Rust Programming} % Subject Area
    {} % Organization (leave empty if not applicable)
    {} % Location (leave empty)
    {} % Dates (leave empty)
    {
      \begin{cvitems}
        \item {Completed the Rustlings exercises, gaining foundational knowledge and experience in Rust.}
        \item {Explored Rust’s type system, pattern matching, and error handling, applying these concepts in small-scale projects.}
        \item {Gained experience working with Rust’s ecosystem, including Cargo package management, unit testing, and build optimizations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Scala Programming} % Subject Area
  {} % Organization (leave empty if not applicable)
  {} % Location (leave empty)
  {} % Dates (leave empty)
  {
    \begin{cvitems}
      \item {Explored the wider ecosystem outside of proprietary HMRC tools, such as Typelevel stack, various libraries such as ScalaCheck, Pureconfig, WeaverTests to name a few.}
      \item {Further improved my understanding of functional programming researching Category Theory, Tagless Final and reading various material on Effect Systems}
      \item {Explored and studied some category theory for the basis of functional programming}
      \item {Familiar with the native library, practicing within my own repositories and making notes on new concepts}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
  {Python Programming} % Subject Area
  {} % Organization (leave empty if not applicable)
  {} % Location (leave empty)
  {} % Dates (leave empty)
  {
    \begin{cvitems}
      \item {Created a playground library called Boxcat hosted on Pypl. Essentially it was to be able to write Python in a functional Scala fashion.}
      \item {Early career built a webscraper, CNN and played with various libraries such as Scikit, Pandas, Matplotlib and Seaborn.}
      \item {Early career studied basic programming concepts and syntax.}
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
{Latex Programming} % Subject Area
{} % Organization (leave empty if not applicable)
{} % Location (leave empty)
{} % Dates (leave empty)
{
  \begin{cvitems}
    \item {Helped develop a friends Phd Thesis.}
    \item {Leared a lot about using Latex, Nix/Nix shell and Vim}
    \item {Used to write my CV special thanks to Claud D. Park. for the base template and then heavily modified to suit my taste and needs}
  \end{cvitems}
}

%---------------------------------------------------------
  % \cventry
  % {Cloud Computing Technologies} % Subject Area
  % {} % Organization (leave empty if not applicable)
  % {} % Location (leave empty)
  % {} % Dates (leave empty)
  % {
  %   \begin{cvitems}
  %     \item {Completed cloud quest lab and workshops.}
  %     \item {Set up VPC,  EC2 instances}
  %     \item {Passing cloud certifications}
  %   \end{cvitems}
  % }

\end{cventries}
